\documentclass[a4paper,12pt,twoside]{article}

\title{Initial Project Proposal\\The importance of physique in NBA}
\author{Tung X. Nguyen\\ID: 30555418\\Tutor: Nicholas Spyrison}
\date{\today}

\setcounter{tocdepth}{3}


\usepackage{apacite}
\usepackage{url}
\usepackage{indentfirst}
\usepackage{amssymb}
\usepackage[showframe=false]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt} 
 
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Tung X. Nguyen}
\fancyhead[RE,LO]{Initial Project Proposal}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[CE,CO]{\leftmark}

\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{1pt}

\begin{document}
\maketitle
\thispagestyle{empty}
\thispagestyle{empty}

\oddsidemargin = 22pt
\evensidemargin = 22pt
\marginparsep = 10pt
\marginparwidth = 35pt


\section{Questions.}

1.1 What is the most common physique type in the NBA (2000-2020)? Do players are getting bigger and stronger as time goes by?

1.2 How physique can affect the draft number of a player (2000-2020)?

1.3 How physique and Player Efficiency Rating correlated (scope: regular season for 2005-2006 and 2018=2019 for comparison)?

1.4 Compare the physique of non-US players to US players (scope: regular season for all seasons)
 


\section{Data source.}
\addcontentsline{toc}{subsection}{}
\begin{itemize}
\item Player Bios Regular Season 
\item Player Efficiency Rating
\end{itemize}

\section{Description of data source}
There are about 450 players in the league in any season.


First source: physique data. Tabular data in HTML with number of rows equal number of players x 20 columns. The data is formatted well for display but not for data explorationi, hence should be wrangled. Also, data across seasons must be merged (union).\\
https://stats.nba.com/players/bio/

Second source:Player Efficiency Rating. Tabular data in HTML with number of rows equal number of players x 14 columns. Data is well formatted, but there is no information of height and weight, therefore require joining with the first source.
\\http://insider.espn.com/nba/hollinger/statistics

\end{document}